### 2022-09-24 LaTeX/MSGARCH.tex
...

% HINZUGEFÜGT VON ADRIAN
% MAKE subsubsubsection possible
\usepackage{titlesec}
\usepackage{cleveref}
\usepackage{acronym}

\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}

@@

\subsection{Markov-Switching Models}

@@

\subsubsection{GARCH}
\label{sss:GARCH}
The \ac{GARCH} model has been popular in order to forecast the volatility of indices. It was introduced XXXX by \cite{} and is an extension of the ARCH model, which was introduced Engle \cite{}. It models the error by using a \ac{ARMA} model.
It tries to explain the observation that the volatility of financial assets tends to be heteroskedastic and cluster, i.e. periods with high volatility are followed by periods with high volatility.

@@

Many extensions of the GARCH model exist which try to account for the the observation that the variance caused by positive returns don't have the same effect as variance that is caused by negative returns. One example is the GJR model by \cite{}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$

@@

\subsection{Data set}

@@

>>>>

% HINZUGEFÜGT VON ADRIAN
% MAKE subsubsubsection possible
\usepackage{titlesec}

\usepackage{cleveref}
\usepackage{acronym}

\graphicspath{{./img/}}

% ACRONYMS 
\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}
\newacro{GED}{Generlized Error Distribution}

@@

$$ \mathcal{L}\left(\Psi \mid \mathcal{I}_T\right) \equiv \prod_{t=1}^T f\left(y_t \mid \Psi, \mathcal{I}_{t-1}\right) $$ 
\subsection{Markov-Switching Models}

@@

\subsubsection{GARCH}
\label{sss:GARCH}
The \ac{GARCH} model has been popular in order to forecast the volatility of indices. It was introduced  by Bollerslev \cite{bollerslev_generalized_1986} and is an extension of the ARCH model, which was introduced Engle \cite{engle_autoregressive_1982}. It models the error by using a \ac{ARMA} model.
It tries to explain the observation that the volatility of financial assets tends to be heteroskedastic and cluster, i.e. periods with high volatility are followed by periods with high volatility.

@@

Many extensions of the GARCH model exist which try to account for the the observation that the variance caused by positive returns don't have the same effect as variance that is caused by negative returns. One example is the GJR model by \cite{glosten_relation_1993}: $$ h_{k, t} \equiv \alpha_{0, k}+\left(\alpha_{1, k}+\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}^2+\beta_k h_{k, t-1}$$

@@

\subsection{Data set}
The GARCH model assumes that the datapoints are equidistant in the time dimension, hence we will use the closing prices of the Index and model the close-to-close variance.

We split our dataset s.t. we use the first 80\% observations for training and the last 20\% for testing the models.

@@

% latex table generated in R 4.1.2 by xtable 1.8-4 package
% Thu Sep 22 19:29:22 2022
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & MSSR1 & MSSR2 & GARCH \\ 
  \hline
$\alpha\_1$ & 0.17 & 0.00 & 0.01 \\ 
  alpha1\_1 & 0.02 & 0.02 & 0.03 \\ 
  alpha2\_1 & 0.21 & 0.08 & 0.08 \\ 
  beta\_1 & 0.75 & 0.94 & 0.92 \\ 
  nu\_1 & 1.05 & 1.53 & 6.19 \\ 
  xi\_1 & 0.86 & 0.96 & 0.93 \\ 
   \hline
\end{tabular}
\end{table}

\subsubsection{Evaluation of Point Forecasts}

\begin{figure}[h]
\includegraphics[width=0.8\linewidth]{pforecast-russia-crash.pdf}
\caption{One-day-ahead volatility forecasts during the Corona crash 2020.}
\end{figure}

\begin{figure}[h]
\includegraphics[width=1.2\linewidth]{FiltVola\_InSample\_Eighties.pdf}
\caption{One-day-ahead volatility forecasts during the Corona crash 2020. MSGARCH is model mostly in state 1.}
\end{figure}

\begin{figure}[h]
\includegraphics[width=1.2\linewidth]{CoronaCrash\_MSGARCH\_Decomposition.pdf}
\caption{One-day-ahead volatility forecasts during the Corona crash 2020. MSGARCH is model mostly in state 1.}
\label{img:cor-decomp}
\end{figure}

In \cref{img:cor-decomp} one can see the two states of the MSGARCH (MSSR1 and MSSR2) model produce different forecasts and how they compare to the stand-alone GARCH model. 
It can be observed that MSSR1 is less persistent, which is due to the smaller $\beta_1 = 0.7519$ compared to the larger $\beta_2 = 0.935$ of MSSR2.
Furthermore we see that MSSR1 has a higher base-level volatility and tends to forecast volatility spikes which are larger than those of MSSR2. This once again, is caused by the larger $\alpha$ values which characterise MSSR1.
